Turbulence in giant HII regions

### 2021-04-22 mnras_template.tex
Javier changes up to April 22

\subsection{Regions in the Milky Way and Large Magellanic Cloud}
\label{sec:regions-milky-way}

We measure the second-order velocity structure function for a number of more compact and lower luminosity regions:
the Orion Nebula \citep{arthur2016turbulence}; 
the Lagoon Nebula \citep{Damiani:2017b};
the Carina Nebula \citep{Damiani:2016a};
the Tarantula Nebula (30~Dor) in the LMC \citep{Castro:2018a}.

In order to study the structure function 
We include

@@

% End of mnras_template.tex
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

@@

% End of mnras_template.tex
